\documentclass[a4paper, 12pt, notitlepage]{report}

\usepackage{amsfonts} % if you want blackboard bold symbols e.g. for real numbers
\usepackage{graphicx} % if you want to include jpeg or pdf pictures

\title{\LaTeX\ Keyword Extraction using Deep Learning Techniques} % change this
\author{Andrew D.A.C. Smith} % change this
\date{\today} % change this

\begin{document}
	
	%%%%%%%%%% PRELIMINARY MATERIAL %%%%%%%%%%
	\maketitle
	\begin{center}
		A project of 20 credit points at level 4. % change this
		\\[12pt]
		Supervised by Dr.\ Arne Kovac. % change this
	\end{center}
	\thispagestyle{empty}
	\newpage
	\section*{Acknowledgement of Sources} % this must be included in undergradate projects
	For all ideas taken from other sources (books, articles, internet), the source of the ideas is mentioned in the main text and fully referenced at the end of the report.
	
	All material which is quoted essentially word-for-word from other sources is given in quotation marks and referenced.
	
	Pictures and diagrams copied from the internet or other sources are labelled with a reference to the web page or book, article etc.
	\\[12pt]
	Signed \dotfill Date \dotfill
	
	\tableofcontents 
	
	%%%%%%%%%% MAIN TEXT STARTS HERE %%%%%%%%%%
	
	%%%%%%%%%% SAMPLE CHAPTER %%%%%%%%%%
	\chapter{The First Chapter}
	%
	The purpose of this document is to provide a template file suitable for a medium-sized undergraduate project.
	Copy the sample chapter as many times as you need.
	It should be obvious how to obtain new sections and subsections.
	Simply replace the existing text with your own 
	
	Rest of the text introducing this chapter.
	
	\section{First section of this chapter}
	%
	The text of this section.
	
	\section{A subsequent section}
	%
	Text introducing this section.
	
	\subsection{First subsection of this section}
	%
	The text of this subsection.
	
	\subsection{Another subsection}
	%
	Text introducing this subsection
	
	\subsubsection{A further subdivision, if necessary}
	%
	Text introducing this subsubsection.
	
	\paragraph{Unnumbered paragraph heading}
	The text of this paragraph.
	
	%%%%%%%%%% INFORMATION %%%%%%%%%%
	\section{A Note About References}
	%
	The Third and Fourth Year Handbook, and the Third and Fourth Year Project Handbook, have some clear guidelines about plagiarism and referencing.
	You should consult your project supervisor about the correct format for handling references.
	
	This document uses the `in-text' or Harvard system of referencing, which is a good default format.
	This requires both in-text citations and a list of references at the end of the document.
	The project templates have an example of a list of references.
	
	Within the text you must cite the authors surname(s) and the date of publication.
	When referring to a specific idea, or a direct quote, you must also give the page number.
	If there are two authors, use `and' and if there are more, use `et al.'\ and give all the authors names at the end.
	
	There are two styles of citation, implicit and explicit.
	Both are equally acceptable and it is also acceptable to mix and match.
	
	\subsection{Examples of implicit in-text citations}
	%
	The sum of convex functions is itself convex (Blacke, 1985) and therefore any minimiser of this objective function will be a global minimiser (Greene and Whit, 1995, p.123). It is possible to exploit this fact (Browne et al., 2005) to enhance the optimisation algorithm.
	
	\subsection{Examples of explicit in-text citations}
	%
	Blacke (1985) first proved that a sum of convex functions is convex. Any minimiser of this objective function will be a global minimiser, a fact shown by Greene and Whit (1995, p.123) and exploited by Browne et al.\ (2005) to enhance the optimisation algorithm.
	
	%%%%%%%%%% APPENDIX %%%%%%%%%%
	\appendix
	\chapter{An Appendix may not be necessary}
	%
	Text introducing the/this appendix.
	
	\section{Appendix section}
	%
	Text of this section.
	
	Subsections and further divisions can also be used in appendices.
	
	%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%
	\chapter*{Bibliography}
	%
	\begin{description}
		
		\item Author, I. (Year). \emph{Book Title}, Publisher; Place of publication.
		
		\item Lamport, L. (1986), \emph{\LaTeX: A Document Preparation System}, Addison-Wesley; Reading, MA.
		
		\item Author, I. (Year). `Journal article title', \emph{Journal}, \textbf{Vol}, pp.first--last.
		
		\item Smith, A.D.A.C. and Wand, M.P. (2008). `Streamlined variance calculations for semiparametric
		mixed models', \emph{Statistics in Medicine}, \textbf{27}, pp.435--48.
		
	\end{description}
	
\end{document}